Switch equivalence and weak prime domains for left-linear DPO rewriting systems

### 2025-02-20 full_version/leftlinear.tex
minori

\begin{lemma}[Uniqueness of switches]
	\label{thm:switch_uni}
	Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^1$ be a derivation and suppose
	that both $\der{E}=\{\dder{E}_i\}_{i=0}^1$ and
	$\der{F}=\{\dder{F}_i\}_{i=0}^1$ are switches of $\dder{D}_0$ and
	$\dder{D}_1$. Then there is an abstraction equivalence between $\der{E}$ and $\der{F}$, whose first component is $\id{G_0}$.
\end{lemma}

\begin{proof}
	By definition of switch $\der{E}_0$ and $\der{F}_0$ have the same match $f_0\circ i_1$ and that $\der{E}_1$ and $\der{F}_1$ have the same comatch $g_1\circ i_0$. Thus we get the solid part of the diagram below
	\[\xymatrix@C=22pt{G_{0} && \ar@{>->}[ll]_{f_{\der{F},0}} D_{\der{F},0} \ar[rr]^{g_{\der{F},0}}&& G_{\der{F},1} && \ar@{>->}[ll]_{f_{\der{F},1}} D_{\der{F},1} \ar[rr]^{g_{\der{F},1}}&& G_{2}\\L_1 \ar[d]^{f_0\circ i_1} \ar[u]_{f_0\circ i_1}&& K_{1} \ar[d]^{k_{\der{E},0}} \ar[u]_{k_{\der{F},0}}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_{1} \ar@/^.35cm/[drrr]|(.315)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{h_{\der{E},0}} \ar@/_.35cm/[urrr]|(.315)\hole^(.4){a_0} \ar[ur]|(.3)\hole^{h_{\der{F},0}}& &L_{0} \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{m_{\der{E},1}} \ar@/^.35cm/[ulll]_(.4){a_1} \ar[ul]|(.3)\hole_{m_{\der{F},1}}& K_{0} \ar[d]_{k_{\der{E},1}} \ar[u]^{k_{\der{F},1}}\ar@{>->}[l]_{l_{0}} \ar[rr]^{r_0} && R_{0} \ar[d]_{g_1\circ i_0} \ar[u]^{g_1\circ i_0}\\ \ar@/^.5cm/[uu]^{\id{G_0}} G_{0} && \ar[ll]^{f_{\der{E},0}} D_{\der{E},0} \ar@{.>}@/^.5cm/[uu]^(.33){\phi_{0}}|\hole \ar[rr]_{g_{\der{E},0}}&& G_{\der{E},1} \ar@{.>}[uu]^(.76){\psi_1}|(.45)\hole |(.55)\hole&& \ar@{>->}[ll]^{f_{\der{E},1}} D_{\der{E},1} \ar@{.>}@/_.5cm/[uu]_(.33){\phi_{1}}|\hole\ar[rr]_{g_{\der{E},1}}&& G_{2}\ar@{.>}@/_.5cm/[uu]_{\psi_2}}\]

@@

	Since $\psi_1$ is an isomorphism, the square below is a pushout. 
	\[\xymatrix{K_0 \ar[d]_{k_{\der{E,1}}} \ar@{>->}[r]^{l_0}& L_0 \ar[d]^{\psi_1\circ m_{\der{E},1}}\\D_{\der{E},1} \ar@{>->}[r]_{\psi_1\circ f_{\der{E},1}}& G_{\der{F}, 1}}\]

@@

\begin{proposition}
	\label{prop:tec}
	Let $(\X,\R)$ be a left-linear rewriting system and
	$(i_0, i_1)$ an independence pair between two direct
	derivations $\dder{D}_0$ and $\dder{D}_1$. Consider the pullback of
	$f_1\colon D_1\mto G_1$ along $g_0\colon D_0\to G_1$ (first
	square below), then there exist the arrows
	$u_1\colon K_1\to P$ and $u_0\colon K_0\to P$ fitting in the
	central and right square. Moreover, the right one is always
	a pullback.
	\[\xymatrix@R=15pt{P \ar@{>->}[r]^{p_0} \ar[d]_{p_1} & D_0
		\ar[d]^{g_0}& K_0 \ar[r]^{r_0} \ar@{.>}[d]_{u_0}& R_0
		\ar[d]^{i_0} & K_1 \ar@{>->}[r]^{l_1} \ar@{.>}[d]_{u_1}&
		L_1 \ar[d]^{i_1}\\ D_1 \ar@{>->}[r]_{f_1} &G_1 &P
		\ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0}
	\]
\end{proposition}

\begin{proof}
	We start noticing that
	\[\begin{split}
	f_1\circ i_0\circ r_0&=h_0\circ r_0\\&=g_0\circ k_0	\end{split}
	 \qquad\begin{split}
	 	g_0\circ i_1\circ l_1&=m_1\circ l_1\\&= f_1 \circ k_1
	 \end{split}
	\]
	Thus there exists the dotted $u_0\colon K_0\to P$,
	$u_1\colon K_1\to P$ in the diagram
	\[\xymatrix@R=15pt{K_0 \ar[d]_{r_0}
		\ar@{.>}[r]_{u_0}\ar@/^.4cm/[rr]^{k_0} &P
		\ar@{>->}[r]_{p_0} \ar[d]_{p_1}& D_0 \ar[d]^{g_0}&K_1
		\ar@{>->}[d]_{l_1}
		\ar@{.>}[r]_{u_1}\ar@/^.4cm/[rr]^{k_1} &P \ar[r]_{p_1}
		\ar@{>->}[d]_{p_0}& D_1 \ar@{>->}[d]^{f_1}\\R_0
		\ar@/_.4cm/[rr]_{h_0}\ar[r]^{i_0}& D_1
		\ar@{>->}[r]^{f_1}& G_1&L_1
		\ar@/_.4cm/[rr]_{m_1}\ar[r]^{i_1}& D_0 \ar[r]^{g_0}&
		G_1}\]
	By \Cref{prop:pbpoad,lem:pb1} we get that the left half of
	the second rectangle is a pullback.
	\qedhere
\end{proof}

\begin{corollary}\label{lem:cose}Let
		$\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation and suppose
		that $(i_0, i_1)$ is an independence pair between $\dder{D}_0$
		and $\der{D}_1$.  If $\der{E}=\{\dder{E}_i\}_{i=0}^1$ is a
		switch of $\der{D}$ along $(i_0, i_1)$, then there exists
		$q_0\colon P\to D_{\der{E},0}$ in the diagram below. 
		\[\xymatrix{D_{\der{E},0} \ar@{>->}[d]_{f_{\der{E},0}}&P
			\ar@{.>}[l]_{q_0} \ar[r]^{p_1} \ar@{>->}[d]_{p_0}& D_1
			\ar@{>->}[d]^{f_1}\\ G_{0}&D_0 \ar@{>->}[l]^{f_0}\ar[r]_{g_0}&
			G_1}\]
		\end{corollary}
\begin{proof}
	Consider the arrow $u_1\colon K_1\to P$ obtained using
	\Cref{prop:tec}. It fits in the big square on the left
	\[		\xymatrix@R=15pt{K_1 \ar[r]^{u_1} \ar@{>->}[d]_{l_1}&P
		\ar[r]^{\id{P}}\ar@{>->}[d]_{p_0}& P\ar@{>->}[d]^{p_0}\\L_1
		\ar[d]_{\id{L_1}}\ar[r]^{i_1}&D_0 \ar[r]^{\id{D_0}}
		\ar[d]_{\id{D_0}}& D_{0} \ar@{>->}[d]^{f_0}&K_1 \ar@{>->}[d]_{l_1}\ar[r]^{k_{\der{E},0}}&
		D_{\der{E},0} \ar@{>->}[d]^{f_{\der{E},0}} & K_1 \ar[r]^{u_1}
		\ar@{>->}[d]_{l_1}& P \ar@{>->}[d]^{f_0\circ
			p_0}\\
		L_1\ar[r]^{i_1} \ar@/_.4cm/[rr]_{m_{\der{E},0}}&D_0
		\ar@{>->}[r]^{f_0}&G_0 & L_1\ar[r]_{m_{\der{E},0}}&G_0 &L_1
		\ar[r]_{m_{\der{E},0}}&G_0}\]

@@

	We say that $(i_0, i_1)$ is a \emph{strong independence pair} if
	the first two squares depicted  
	below are pushouts and if the pushout of $r_1 : K_1 \to R_1$ along $u_1 : K_1 \to P$ exists.
	\[
	\xymatrix@R=16pt{
		K_0 \ar[r]^{r_0} \ar[d]_{u_0}& R_0 \ar[d]^{i_0} & K_1
		\ar@{>->}[r]^{l_1} \ar[d]_{u_1}& L_1 \ar[d]^{i_1}
		&K_1 \ar[r]^{r_1} \ar[d]_{u_1}& R_1\ar@{.>}[d]^{j_0}
		\\
		%
		P \ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0
		& P \ar@{.>}[r]_{q_1} & Q_1
	}
	\]
\end{definition}

\begin{remark}\label{rem:deco} 
	Let $(i_0, i_1)$ be a strong
	independence pair between the direct derivations $\dder{D}_0$ and
	$\dder{D}_1$. We can then build the solid part of the diagram
	below
	\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
		\ar[dr]^{h_0}&& L_1\ar@/^.8cm/[ddll]^(.2){i_1}
		\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
		\ar@/_.6cm/[ddrr]^(.65){u_0}\ar[ur]^{r_0}&& G_1 && K_1
		\ar@/^.6cm/[ddll]_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
		\ar[dr]^{r_1}\\L_0 \ar[dr]^{m_0}
		\ar@{.>}@/_.6cm/[ddrr]_{j_1}&& D_0
		\ar@{>->}[dl]|(.42)\hole_(.64){f_0}\ar[ur]|(.48)\hole^(.7){g_1}&&D_1
		\ar[dr]|(.42)\hole^(.65){g_1}
		\ar@{>->}[ul]|(.48)\hole_(.7){f_1}&&R_1\ar@/^.6cm/[ddll]^{j_0}\ar[dl]^{h_1}\\&G_0
		&&P\ar[dr]^{q_1}
		\ar@{>.>}[dl]_{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\&&Q_0
		\ar@{>->}@{>.>}[ul]_{a_0} &&Q_1\ar@{.>}[ur]^{b_1}}
	\]

	Let us complete this diagram defining the dotted arrows. To get
	$j_1\colon L_0\to Q_0$ and $q_0\colon P\to Q_0$ it is enough to
	take a pushout of $l_0$ along $u_0$, which exists since
	$l_0\in \mathcal{M}$. Moreover, the existence of the wanted
	$a_0\colon Q_0\to G_0$ and $b_1\colon Q_1\to G_2$ follows from
	\[\begin{split}
	f_0\circ p_0 \circ u_0 &= f_0\circ k_0 \\&= m_0\circ l_0
	\end{split}
	 \qquad\begin{split}
	 	g_1\circ p_1\circ u_1 &= g_1\circ k_1\\&=h_1\circ r_1
	 \end{split}
	\]
	We can prove some other properties of
		the arrows appearing in the diagram above. The four rectangles
		below are pushouts and their left halves are pushouts
		too. Therefore, by \Cref{lem:po1} also their right halves are
		pushouts.  Moreover, $q_0$ and $a_0$ are pushouts of
		respectively $l_0$ and $p_0$, thus they are elements of
		$\mathcal{M}$. By \Cref{prop:pbpoad} the left halves of the
		first and third rectangles are pullbacks too.

@@

\begin{theorem}[Local Church-Rosser Theorem]\label{prChurch} Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a left-linear DPO rewriting system on it. If $(i_0, i_1)$ is a strong independence pair
	between $\dder{D}_0$ and $\dder{D}_1$, then there exists a switch of $\dder{D}_0$ and $\dder{D}_1$ along it.
\end{theorem}
\begin{proof}
	Let us begin considering the diagram
	built in \Cref{rem:deco}
	\[\xymatrix@C=15pt@R=15pt{&&R_0
		\ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole \ar[dr]^{h_0}&&
		L_1\ar@/^.8cm/[ddll]^(.2){i_1}
		\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
		\ar@/_.6cm/[ddrr]^(.65){u_0}\ar[ur]^{r_0}&& G_1 && K_1
		\ar@/^.6cm/[ddll]_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
		\ar[dr]^{r_1}\\L_0 \ar[dr]^{m_0} \ar@{>}@/_.6cm/[ddrr]_{j_1}&& D_0
		\ar@{>->}[dl]|(.42)\hole_(.64){f_0}\ar[ur]|(.48)\hole^(.7){g_1}&&D_1
		\ar[dr]|(.42)\hole^(.65){g_1}
		\ar@{>->}[ul]|(.48)\hole_(.7){f_1}&&R_1\ar@/^.6cm/[ddll]^{j_0}\ar[dl]_{h_1}\\&G_0
		&&P\ar[dr]^{q_1}
		\ar@{>->}[dl]_{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\&&Q_0
		\ar@{>->}@{>->}[ul]_{a_0} \ar@{.>}[dr]_{b_0} &&Q_1\ar[ur]^{b_1}
		\ar@{>.>}[dl]^{a_1} \\ &&&H_1 }\] Since $q_0\colon P\to Q_0$ is in
	$\mathcal{M}$, we can take its pushout along $q_1$ to get the dotted
	arrows $a_1\colon Q_1\mto H_1$ and $q_0\colon Q_0\to H_1$. But then,
	since the composite of two pushout squares is a pushout, the diagram
	below is a derivation
	\[\xymatrix{L_1 \ar[d]_{f_0 \circ i_1}&& K_1
		\ar[d]_{q_0\circ u_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1
		\ar@/^.35cm/[drrr]|(.31)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{a_1\circ
			j_0} && L_0 \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{b_0\circ
			j_1}& K_1 \ar[d]^{q_1\circ u_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0
		\ar[d]^{g_1\circ i_0} \\G_0 && \ar@{>->}[ll]^{a_0} Q_0 \ar[rr]_{b_0}&&
		H_1 && \ar@{>->}[ll]^{a_1} Q_1 \ar[rr]_{b_1}&& G_2}\] It is immediate
	now to see that it is a switch of $\dder{D}_0$ and $\dder{D}_1$ along
	$(i_0, i_1)$.
\end{proof}

@@

\begin{corollary}\label{cor:strongip}
	Let $(\X, \R)$ be a left-linear DPO rewriting system and consider the following derivation $\der{D}={\dder{D}_{i}}_{i=0}^i$ and suppose that $(i_0, i_1)$ is a strong independence pair.
	\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0
		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
		\ar@{.>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{.>}@/_.25cm/[dlll]^(.4){i_1}
		\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
		\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
		D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
		\ar[rr]_{g_1}&& G_2}
	\]

>>>>

\begin{lemma}[Uniqueness of switches]
	\label{thm:switch_uni}
	Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^1$ be a derivation and suppose
	that both $\der{E}=\{\dder{E}_i\}_{i=0}^1$ and
	$\der{F}=\{\dder{F}_i\}_{i=0}^1$ are switches of $\dder{D}_0$ and
	$\dder{D}_1$. Then there is an abstraction equivalence $\{\phi_X\}_{X\in \Deltamin(\der{E})}$ between $\der{E}$ and $\der{F}$, whose first component is $\id{G_0}$. Moreover, 
	\[\phi_{D_{\der{E}, 0}}\circ j_1=a_1 \qquad \phi_{\der{E}, 1}\circ j_0=a_0\]
\end{lemma}

\begin{proof}
	By definition of switch $\der{E}_0$ and $\der{F}_0$ have the same match $f_0\circ i_1$ and that $\der{E}_1$ and $\der{F}_1$ have the same comatch $g_1\circ i_0$. Thus we get the solid part of the diagram below. If we are able to construct the dotted arrow and prove that they are isomorphism we are done.
	\[\xymatrix@C=22pt{G_{0} && \ar@{>->}[ll]_{f_{\der{F},0}} D_{\der{F},0} \ar[rr]^{g_{\der{F},0}}&& G_{\der{F},1} && \ar@{>->}[ll]_{f_{\der{F},1}} D_{\der{F},1} \ar[rr]^{g_{\der{F},1}}&& G_{2}\\L_1 \ar[d]^{f_0\circ i_1} \ar[u]_{f_0\circ i_1}&& K_{1} \ar[d]^{k_{\der{E},0}} \ar[u]_{k_{\der{F},0}}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_{1} \ar@/^.35cm/[drrr]|(.315)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{h_{\der{E},0}} \ar@/_.35cm/[urrr]|(.315)\hole^(.4){a_0} \ar[ur]|(.3)\hole^{h_{\der{F},0}}& &L_{0} \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{m_{\der{E},1}} \ar@/^.35cm/[ulll]_(.4){a_1} \ar[ul]|(.3)\hole_{m_{\der{F},1}}& K_{0} \ar[d]_{k_{\der{E},1}} \ar[u]^{k_{\der{F},1}}\ar@{>->}[l]_{l_{0}} \ar[rr]^{r_0} && R_{0} \ar[d]_{g_1\circ i_0} \ar[u]^{g_1\circ i_0}\\ \ar@/^.5cm/[uu]^{\id{G_0}} G_{0} && \ar[ll]^{f_{\der{E},0}} D_{\der{E},0} \ar@{.>}@/^.5cm/[uu]^(.33){\phi_{0}}|\hole \ar[rr]_{g_{\der{E},0}}&& G_{\der{E},1} \ar@{.>}[uu]^(.76){\psi_1}|(.45)\hole |(.55)\hole&& \ar@{>->}[ll]^{f_{\der{E},1}} D_{\der{E},1} \ar@{.>}@/_.5cm/[uu]_(.33){\phi_{1}}|\hole\ar[rr]_{g_{\der{E},1}}&& G_{2}\ar@{.>}@/_.5cm/[uu]_{\psi_2}}\]

@@

	Since $\psi_1$ is an isomorphism, the square below is a pushout. 
	\[\xymatrix@C=35pt{K_0 \ar[d]_{k_{\der{E},1}} \ar@{>->}[r]^{l_0}& L_0 \ar[d]^{\psi_1\circ m_{\der{E},1}}\\D_{\der{E},1} \ar@{>->}[r]_{\psi_1\circ f_{\der{E},1}}& G_{\der{F}, 1}}\]

@@

\begin{proposition}
	\label{prop:tec}
	Let $(\X,\R)$ be a left-linear rewriting system and
	$(i_0, i_1)$ an independence pair between two direct
	derivations $\dder{D}_0$ and $\dder{D}_1$. Consider the pullback of
	$f_1\colon D_1\mto G_1$ along $g_0\colon D_0\to G_1$ (first
	square below), then there exist the arrows
	$u_1\colon K_1\to P$ and $u_0\colon K_0\to P$ fitting in the
	central and right square. Moreover, the right one is always
	a pullback.
	\[\xymatrix{P \ar@{>->}[r]^{p_0} \ar[d]_{p_1} & D_0
		\ar[d]^{g_0}& K_0 \ar[r]^{r_0} \ar@{.>}[d]_{u_0}& R_0
		\ar[d]^{i_0} & K_1 \ar@{>->}[r]^{l_1} \ar@{.>}[d]_{u_1}&
		L_1 \ar[d]^{i_1}\\ D_1 \ar@{>->}[r]_{f_1} &G_1 &P
		\ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0}
	\]
\end{proposition}

\begin{proof}
	We start noticing that
	\[\begin{split}
	f_1\circ i_0\circ r_0&=h_0\circ r_0\\&=g_0\circ k_0	\end{split}
	 \qquad\begin{split}
	 	g_0\circ i_1\circ l_1&=m_1\circ l_1\\&= f_1 \circ k_1
	 \end{split}
	\]
	Thus there exists the dotted $u_0\colon K_0\to P$,
	$u_1\colon K_1\to P$ in the diagram
	\[\xymatrix{K_0 \ar[d]_{r_0}
		\ar@{.>}[r]_{u_0}\ar@/^.4cm/[rr]^{k_0} &P
		\ar@{>->}[r]_{p_0} \ar[d]_{p_1}& D_0 \ar[d]^{g_0}&K_1
		\ar@{>->}[d]_{l_1}
		\ar@{.>}[r]_{u_1}\ar@/^.4cm/[rr]^{k_1} &P \ar[r]_{p_1}
		\ar@{>->}[d]_{p_0}& D_1 \ar@{>->}[d]^{f_1}\\R_0
		\ar@/_.4cm/[rr]_{h_0}\ar[r]^{i_0}& D_1
		\ar@{>->}[r]^{f_1}& G_1&L_1
		\ar@/_.4cm/[rr]_{m_1}\ar[r]^{i_1}& D_0 \ar[r]^{g_0}&
		G_1}\]
	By \Cref{prop:pbpoad,lem:pb1} we get that the left half of
	the second rectangle is a pullback.
	\qedhere
\end{proof}

\begin{corollary}\label{lem:cose}Let
		$\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation and suppose
		that $(i_0, i_1)$ is an independence pair between $\dder{D}_0$
		and $\der{D}_1$.  If $\der{E}=\{\dder{E}_i\}_{i=0}^1$ is a
		switch of $\der{D}$ along $(i_0, i_1)$, then there exists
		$q_0\colon P\to D_{\der{E},0}$ in the diagram below. 
		\[\xymatrix{D_{\der{E},0} \ar@{>->}[d]_{f_{\der{E},0}}&P
			\ar@{.>}[l]_{q_0} \ar[r]^{p_1} \ar@{>->}[d]_{p_0}& D_1
			\ar@{>->}[d]^{f_1}\\ G_{0}&D_0 \ar@{>->}[l]^{f_0}\ar[r]_{g_0}&
			G_1}\]
		\end{corollary}
\begin{proof}
	Consider the arrow $u_1\colon K_1\to P$ obtained using
	\Cref{prop:tec}. It fits in the big square on the left
	\[		\xymatrix{K_1 \ar[r]^{u_1} \ar@{>->}[d]_{l_1}&P
		\ar[r]^{\id{P}}\ar@{>->}[d]_{p_0}& P\ar@{>->}[d]^{p_0}\\L_1
		\ar[d]_{\id{L_1}}\ar[r]^{i_1}&D_0 \ar[r]^{\id{D_0}}
		\ar[d]_{\id{D_0}}& D_{0} \ar@{>->}[d]^{f_0}&K_1 \ar@{>->}[d]_{l_1}\ar[r]^{k_{\der{E},0}}&
		D_{\der{E},0} \ar@{>->}[d]^{f_{\der{E},0}} & K_1 \ar[r]^{u_1}
		\ar@{>->}[d]_{l_1}& P \ar@{>->}[d]^{f_0\circ
			p_0}\\
		L_1\ar[r]^{i_1} \ar@/_.4cm/[rr]_{m_{\der{E},0}}&D_0
		\ar@{>->}[r]^{f_0}&G_0 & L_1\ar[r]_{m_{\der{E},0}}&G_0 &L_1
		\ar[r]_{m_{\der{E},0}}&G_0}\]

@@

	We say that $(i_0, i_1)$ is a \emph{strong independence pair} if
	the first two squares depicted  
	below are pushouts and if the pushout of $r_1 : K_1 \to R_1$ along $u_1 : K_1 \to P$ exists.
	\[
	\xymatrix{
		K_0 \ar[r]^{r_0} \ar[d]_{u_0}& R_0 \ar[d]^{i_0} & K_1
		\ar@{>->}[r]^{l_1} \ar[d]_{u_1}& L_1 \ar[d]^{i_1}
		&K_1 \ar[r]^{r_1} \ar[d]_{u_1}& R_1\ar@{.>}[d]^{j_0}
		\\
		%
		P \ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0
		& P \ar@{.>}[r]_{q_1} & Q_1
	}
	\]
\end{definition}

\begin{remark}\label{rem:deco} 
	Let $(i_0, i_1)$ be a strong
	independence pair between the direct derivations $\dder{D}_0$ and
	$\dder{D}_1$. We can then build the solid part of the diagram
	below
	\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
		\ar[dr]^{h_0}&& L_1\ar@/^.8cm/[ddll]^(.2){i_1}
		\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
		\ar@/_.6cm/[ddrr]_(.65){u_0}\ar[ur]^{r_0}&& G_1 && K_1
		\ar@/^.6cm/[ddll]^(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
		\ar[dr]^{r_1}\\L_0 \ar[dr]^{m_0}
		\ar@{.>}@/_.6cm/[ddrr]_{j_1}&& D_0
		\ar@{>->}[dl]|(.42)\hole_(.64){f_0}\ar[ur]|(.48)\hole^(.7){g_1}&&D_1
		\ar[dr]|(.42)\hole^(.65){g_1}
		\ar@{>->}[ul]|(.48)\hole_(.7){f_1}&&R_1\ar@/^.6cm/[ddll]^{j_0}\ar[dl]^{h_1}\\&G_0
		&&P\ar[dr]^{q_1}
		\ar@{>.>}[dl]_{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\&&Q_0
		\ar@{>->}@{>.>}[ul]_{a_0} &&Q_1\ar@{.>}[ur]^{b_1}}
	\]

	Let us complete this diagram defining the dotted arrows. To get
	$j_1\colon L_0\to Q_0$ and $q_0\colon P\to Q_0$ it is enough to
	take a pushout of $l_0$ along $u_0$, which exists since
	$l_0\in \mathcal{M}$. Moreover, the existence of the wanted
	$a_0\colon Q_0\to G_0$ and $b_1\colon Q_1\to G_2$ follows from
	\[\begin{split}
	f_0\circ p_0 \circ u_0 &= f_0\circ k_0 \\&= m_0\circ l_0
	\end{split}
	 \qquad\begin{split}
	 	g_1\circ p_1\circ u_1 &= g_1\circ k_1\\&=h_1\circ r_1
	 \end{split}
	\]
	We can prove some other properties of
		the arrows appearing in the diagram above. The four rectangles
		below are pushouts and their left halves are pushouts
		too. Therefore, by \Cref{lem:po1} also their right halves are
		pushouts.  Moreover, $q_0$ and $a_0$ are pushouts of
		respectively $l_0$ and $p_0$, thus they are elements of
		$\mathcal{M}$. By \Cref{prop:pbpoad} the left halves of the
		second and third rectangles are pullbacks too.

@@

\begin{theorem}[Local Church-Rosser Theorem]\label{prChurch} Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a left-linear DPO rewriting system on it. If $(i_0, i_1)$ is a strong independence pair
	between $\dder{D}_0$ and $\dder{D}_1$, then there exists a switch of $\dder{D}_0$ and $\dder{D}_1$ along it.
\end{theorem}
\begin{proof}
	Let us begin considering the diagram
	built in \Cref{rem:deco}
	\[\xymatrix@C=15pt@R=15pt{&&R_0
		\ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole \ar[dr]^{h_0}&&
		L_1\ar@/^.8cm/[ddll]^(.2){i_1}
		\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
		\ar@/_.6cm/[ddrr]_(.65){u_0}\ar[ur]^{r_0}&& G_1 && K_1
		\ar@/^.6cm/[ddll]^(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
		\ar[dr]^{r_1}\\L_0 \ar[dr]^{m_0} \ar@{>}@/_.6cm/[ddrr]_{j_1}&& D_0
		\ar@{>->}[dl]|(.42)\hole_(.64){f_0}\ar[ur]|(.48)\hole^(.7){g_1}&&D_1
		\ar[dr]|(.42)\hole^(.65){g_1}
		\ar@{>->}[ul]|(.48)\hole_(.7){f_1}&&R_1\ar@/^.6cm/[ddll]^{j_0}\ar[dl]_{h_1}\\&G_0
		&&P\ar[dr]^{q_1}
		\ar@{>->}[dl]_{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\&&Q_0
		\ar@{>->}@{>->}[ul]_{a_0} \ar@{.>}[dr]_{b_0} &&Q_1\ar[ur]^{b_1}
		\ar@{>.>}[dl]^{a_1} \\ &&&H_1 }\]

		Since $q_0\colon P\to Q_0$ is in
	$\mathcal{M}$, we can take its pushout along $q_1$ to get the dotted
	arrows $a_1\colon Q_1\mto H_1$ and $q_0\colon Q_0\to H_1$. But then,
	since the composite of two pushout squares is a pushout, the diagram
	below is a derivation
	\[\xymatrix{L_1 \ar[d]_{f_0 \circ i_1}&& K_1
		\ar[d]_{q_0\circ u_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1
		\ar@/^.35cm/[drrr]|(.31)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{a_1\circ
			j_0} && L_0 \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{b_0\circ
			j_1}& K_0 \ar[d]^{q_1\circ u_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0
		\ar[d]^{g_1\circ i_0} \\G_0 && \ar@{>->}[ll]^{a_0} Q_0 \ar[rr]_{b_0}&&
		H_1 && \ar@{>->}[ll]^{a_1} Q_1 \ar[rr]_{b_1}&& G_2}\]

		The thesis now follows at once since, by construction, the derivation above is a switch of $\dder{D}_0$ and $\dder{D}_1$ along	$(i_0, i_1)$.
\end{proof}

@@

\begin{lemma}\label{cor:strongip}
	Let $(\X, \R)$ be a left-linear DPO rewriting system and consider the following derivation $\der{D}={\dder{D}_{i}}_{i=0}^i$ and suppose that $(i_0, i_1)$ is a strong independence pair.
	\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0
		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
		\ar@{.>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{.>}@/_.25cm/[dlll]^(.4){i_1}
		\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
		\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
		D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
		\ar[rr]_{g_1}&& G_2}
	\]

	Suppose, moreover, that the following diagram defines a switch for $\dder{D}_0$ and $\dder{D}_1$ along $(i_0, i_1)$. 	
	\[
	\xymatrix@R=20pt@C=20pt{
		{L_1} \ar[d]_{m_0'}
		&&  {K_1} \ar@{>->}[ll]_{l_1} \ar[r]^{r_1} \ar[d]_{k_0'}
		&  {R_1} \ar[dr]|(.33)\hole_{h_0'}  \ar@/^.25cm/@{.>}_(.4){i_0'}|(.32)\hole[drrr]
		& & 
		{L_0}\ar[dl]|(.33)\hole^{m_1'} \ar@/_.25cm/@{.>}^(.4){i_1'}[dlll] 
		&  {K_0} \ar@{>->}[l]_{l_0} \ar[rr]^{r_0} \ar[d]^{k_1'}
		& & {R_0} \ar[d]^{h_1'} \\		
		{G_0}
		& & {D_0'} \ar@{>->}[ll]^{f_0'} \ar[rr]_{g_0'}
		& &  {G'_1} 
		& &  {D_1'} \ar@{>->}[ll]^{f_1'} \ar[rr]_{g_1'}
		& & {G_2}  }
	\]
and define $T$, with the arrows $t_0\colon T\mto D'_0$ and $t_1\colon T\to D'_1$ as the pullback of $f'_1$ along $g'_0$.
